A better way to format your document for CEUR-WS

### 2024-05-28 paper/sections/04-method.tex
general small updates

\subsubsection{Principal Component Analysis}
Principal Component Analysis (PCA) is a method for reducing dimensionality

>>>>

\subsubsection{Principal Component Analysis}
Principal Component Analysis (PCA) is a method for reducing dimensionality~\cite{pcapaper}. It functions by projecting the high dimensional data onto the direction of maximum variance, thus retaining key features and reducing noise.
